VOCC outline

### 2020-04-11 ms/ms.Rmd
add draft figs to ms

```{r worm-plots, fig.cap="Caption goes here", out.width="8in"}
# include_graphics(here("ms", "figs", "worm-plots.pdf"))
```

@@

```{r do-chops, fig.cap="Caption goes here", out.width="8in"}
include_graphics(here("ms", "figs", "do-chops.pdf"))
```

>>>>

```{r worm-plots, fig.cap="Caption goes here", out.width="8in"}
# include_graphics(here("ms", "figs", "worm-plot-trend.pdf")) # 
include_graphics(here("ms", "figs", "worm-plot-both.pdf"))
```

@@

```{r do-chops, fig.cap="Caption goes here", out.width="8in"}
# include_graphics(here("ms", "figs", "do-chops.pdf"))
```

```{r slope-by-depth, fig.cap="Caption goes here", out.width="5in"}
include_graphics(here("ms", "figs", "slope-by-depth.pdf"))
```

```{r coef-scatterplots, fig.cap="Caption goes here", out.width="8in"}
include_graphics(here("ms", "figs", "coef-scatterplots.pdf"))
```
